\input{content/constants}
\newcommand{\Company}{}
% recipient data
\recipient{\phantom{.}}{}
\date{}
% \enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle{}

Building AI systems that balance technical rigor with human impact has defined my journey—from developing reinforcement learning frameworks at Seoul National University to revitalizing the arts on campus as a student leader. As an AI engineer and recent graduate, I've thrived in roles demanding both precision and creativity, and I'm eager to bring this dual perspective to your team.


At SNU's Vision \& Learning Lab, I engineered a reinforcement learning environment that reduced task evaluation overhead to 1.7\% of runtime, while mentoring peers to adopt JAX/Flax workflows (25\% lab-wide adoption in one year). Beyond purely technical roles, I've designed open-source tools like RL-THOR to facilitate AI research and led cross-functional initiatives—whether teaching 150+ students or coordinating national sports competitions for 1.8K participants. These experiences equipped me to bridge technical rigor with team-driven execution, delivering solutions that balance innovation and practical constraints.

What excites me most is solving problems where scalable engineering meets real-world complexity. My work has straddled France and South Korea, blending academic rigor with a global outlook—a mindset I believe is critical for building inclusive, forward-thinking AI solutions.

I would be thrilled to explore how my skills in Python, Rust, and AI/ML system design can support your mission, and contribute to building thoughtful, scalable solutions.

Thank you for your consideration.

\makeletterclosing
