\input{content/constants}
\newcommand{\Company}{Hi!Paris}
% recipient data
\recipient{\RecruitmentTeam{\Company}}{\Company\\Palaiseau\\ France}
\date{April 22 2025}
% \enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

Some of the most fulfilling moments in my career have come from bridging the gap between technical innovation and societal impact — a mission at the very heart of Hi! PARIS.

With academic training in both Data Science and Computer Science from École des Mines de Saint-Étienne and Seoul National University, I bring hands-on experience in developing machine learning solutions, deploying models with tools like Docker and GitHub Actions, and collaborating on interdisciplinary projects. I thrive in research-driven environments and have supported initiatives that span both academic and applied domains.

The opportunity to contribute to Hi! PARIS’ four pillars — particularly by supporting professors and researchers, engaging in educational initiatives like the Data Bootcamp, and contributing to socially responsible AI projects — aligns deeply with my professional aspirations and values.

I am excited about the vision of Hi! PARIS Cluster 2030 and eager to support its engineering efforts to further elevate France’s global leadership in AI.

Thank you for considering my application. I would be honored to contribute to this ambitious and collaborative mission.

\makeletterclosing
