\input{content/constants}
\newcommand{\Company}{Microsoft}
% recipient data
\recipient{\RecruitmentTeam{\Company}}{\Company\\Washington\\ United States}
% \date{April 28 2025}
% \enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

As an avid “learn-it-all” passionate about ethical AI, I’m drawn to Microsoft’s mission to empower progress through technology that prioritizes reliability and inclusivity. My experience aligns with your focus on scalable, responsible AI systems.

At Seoul National University’s Vision \& Learning Lab, I reduced AI task evaluation overhead to 1.7\% of runtime via a modular framework and mentored researchers to achieve 25\% lab-wide adoption of JAX/Flax workflows—showcasing my ability to optimize systems while fostering team growth. My open-source RL-THOR project further reflects my commitment to building tools that balance research depth with usability, a core tenet of Microsoft’s platform philosophy.

Beyond code, I’ve bridged technical and human challenges: guiding 150+ students as a teaching assistant and spearheading campus arts engagement as a student leader. These roles reinforced my belief that impactful innovation thrives at the intersection of precision and empathy—a synergy mirrored in Microsoft’s culture.

I’m eager to bring my technical rigor, collaborative mindset, and dedication to responsible AI to your team. Let’s engineer solutions that scale thoughtfully and empower globally.

Thank you for your consideration.

\makeletterclosing
