\input{content/constants}
\newcommand{\Company}{Corsearch}
% recipient data
\recipient{\RecruitmentTeam{\Company}}{\Company\\Paris\\ France}
% \date{April 5 2025}
% \enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

As an AI engineer with a focus on risk-aware systems, I am drawn to IGAD’s mission of enhancing audit precision through data science. My experience in Python, collaborative problem-solving, and technical mentorship aligns with your needs for a VIE Data Scientist.

At Seoul National University’s AI lab, I optimized reinforcement learning environments to reduce evaluation overhead to 1.3\% of the simulation runtime, while training researchers in scalable workflows—a balance of innovation and knowledge-sharing I’d bring to auditing teams. During my internship at Apex Solutions, I designed secure RL frameworks under strict data constraints, mirroring the sensitivity of audit protocols.

Leadership roles, including reviving campus arts engagement as Art Council President, honed my ability to build inclusive communities—a skill I’d apply to animating IGAD Asia’s data network and upskilling auditors. Fluent in English and intermediate in Korean, I thrive in cross-cultural settings like Hong Kong.

Société Générale’s emphasis on responsibility and innovation resonates with my approach to technology. IGAD’s R\&D focus excites me, as does the chance to contribute to tools that transform risk management.

I would be honored to support your third line of defense with both technical rigor and collaborative energy.


\makeletterclosing
