% Education section

\companyNameAndLocationHeading{
    Seoul National University, College of Engineering
    \(|\)
    % \small{Seoul, South Korea}
    \small{\IfLanguageName{french}{Corée du Sud}{South Korea}}
}{
    \textit{\september{} 2022 \textbf{--} \july{} 2024}
}
\titleAndDateHeading{

    Master of Computer Science and Engineering (\IfLanguageName{french}{Double Diplôme}{Double Degree})
}{
    % \textbf{GPA: 3.3/4.0} % chktex 13
}
\outerBulletListStart{}
\bulletItem{
    \textbf{\iflanguage{french}{Mémoire de Master}{Master Thesis}:}
    RL-THOR: A Training Ground for Embodied  % ChkTeX 13
    Reinforcement Learning Agents on
    Compositional Household Tasks
}
\bulletItem{
    \textbf{\IfLanguageName{french}{Cours Principaux}{Relevant Courses}:}
    Machine Learning (ML),
    Natural Language Processing (NLP),
    Probabilistic Graphical Model,
    Advanced Computer Architecture.
}
\bulletItem{
    \textbf{\iflanguage{french}{Assistant d'Enseigenement}{Teacher Assistant Work}:}
    \innerBulletListStart{}
    \bulletItem{
        \iflanguage{french}{
            \textbf{Modèles Graphiques Probabilistes (cycle supérieur):}
            Conception et correction d'un examen de mi-trimestre et d'evaluations hebdomadaires (\midTilde40 étudiants).
        }{
            \textbf{Probabilistic Graphical Model (Graduate):}
            Designed and graded one midterm exam and regular quizzes for a class of \midTilde40 students.
        }}
    \bulletItem{
        \iflanguage{french}{
            \textbf{Mathématiques Discrètes (cycle inférieur):} Conception, supervision et correction d'un partiel de 2h et de plusieurs devoirs (\(\sim{}\)150 étudiants).
        }{
            \textbf{Discrete Math (Undergraduate):}
            Designed, administered, and graded a 2-hour final exam and two major homework assignments for \midTilde150 students.
        }
    }
    \innerBulletListEnd{}
}
\outerBulletListEnd{}

\companyNameAndLocationHeading{
    École Nationale Supérieure des Mines de Saint-Étienne % (EMSE)
    \(|\)
    % \small{Saint-Étienne, France}
    \small{France}
}{
    \textit{\september{} 2020 \textbf{--} \september{}  2024}
}
\titleAndDateHeading{
    \iflanguage{french}{
        Diplôme d'Ingénieur Civil des Mines (ICM) en Science des Données % chktex 19
    }{
        Master of Data Science; Diplôme d'Ingénieur Civil des Mines (ICM) % chktex 19
    }

}{
    % \textbf{GPA: 3.3/4.0} % chktex 13
}
\outerBulletListStart{}
\bulletItem{
    \iflanguage{french}{
        \textbf{Cours Principaux:}
        Probabilité \& Statistiques,
        Apprentissage Statistique,
        Machine learning,
        Métamodélisation et optimisation,
        Intelligence Artificielle,
        Traitement d'Images,
        Réseau,
        % Quantum Computing,
        % Méthodes Expérimentales.
    }{
        \textbf{Relevant Courses:}
        Probability \& Statistics,
        Statistical learning,
        Machine learning,
        Metamodeling and Optimization,
        Artificial Intelligence,
        Image Processing,
        Networks,
        % Quantum Computing,
        % Experimental methods.
    }
}
\bulletItem{
    \iftoggle{with_award}
    {
        \textbf{\iflanguage{french}{Prix de l'Engagement Associatif}{Award for Community Engagement:}}
    }{
        \textbf{\iflanguage{french}{Engagement Associatif}{Community Engagement:}}
    }
    \innerBulletListStart{}
    \bulletItem{
        \iflanguage{french}{
            \textbf{President, Bureau des Arts:}
            Direction de la programmation culturelle, incluant l'organisation de trois événements majeurs par mois et la production du gala annuel réunissant plus de 100 artistes.
            Nombre d'adhérents doublé en un an.


        }{
            \textbf{President, Arts Council (Bureau des Arts):}
            Directed cultural programming and events, organizing three monthly events, including the school's annual gala featuring over 100 artists.
            Expanded arts engagement through regular music, dance, and theater classes, doubling participant numbers over one year.
        }
    }
    \bulletItem{\iflanguage{french}{
            \textbf{Responsable des Sports, Cartel des Mines 2022:}
            Coordination de la compétition d'un événement multisportif inter-écoles (4 jours, 14 sports, 1800+ participants, 150 000 € de budget), recevant un taux de satisfaction élevé des participants.
        }{
            \textbf{Sports Coordinator, Cartel des Mines 2022:}
            Directed the logistical and athletic planning of a 4-day inter-school multi-sport competition (14 sports, 1,800+ participants, \$160,000 budget), achieving high participant satisfaction.
        }
    }
    \innerBulletListEnd{}
}
\outerBulletListEnd{}
