\section{\iflanguage{french}{Expériences}{Experiences}}
% \subsection{Vocational}
\cventry{
	2022--2024
}{
	\iflanguage{french}{Étudiant-chercheur}{Graduate Student Researcher}%
}{%
	SNU Vision \& Learning Lab
}{%
	% \Seoul%
}{}{
	\iflanguage{french}{
		\begin{itemize}
			\item Conception d'un framework d'entraînement d'IA domestiques et déploiement d'un environnement d'apprentissage par renforcement.
			      % Implementation de modèles de deep learning en JAX et formation de chercheurs à JAX\@.
			\item Formation de chercheurs au framework de machine learning \emph{JAX}\@.
			\item Assistant d'enseignement en \emph{Mathématiques Discrètes} et \emph{Modèles Graphiques Probabilistes}.
			      %   Conception et correction de sujets d'examens.
		\end{itemize}
	}{
		\begin{itemize}
			% \item Designed and deployed a reinforcement learning (RL) framework for training domestic AI agents, including a custom RL environment based on AI2THOR for hierarchical task simulation.
			% \item Optimized a probabilistic graphical model for unsupervised skill extraction using JAX/Flax and RLHF, reducing training costs by 60\%.
			% \item Mentored 10+ researchers on adopting JAX, achieving 25\% lab-wide adoption within one year.
			% \item Deployed Docker containers to run Unity-based simulations on a headless cluster, cutting agent evaluation overhead to 1.7\% of raw simulation runtime.
			% \item Teaching Assistant for Discrete Mathematics (Undergraduate) and Probabilistic Graphical Models (Graduate):
			%       - Discrete Mathematics: Designed, administered, and graded a 2-hour final exam and 2 homework assignments for a class of 150+ students.
			%       - Probabilistic Graphical Models: Created and graded 1 midterm exam and weekly quizzes for 40+ graduate students.
			\item Designed and deployed a domestic AI training framework with reinforcement learning (RL) environment, including an AI2THOR-based environment for hierarchical tasks (evaluation overhead reduced to 1.7\% of raw runtime).
			      % \item Trained researchers on JAX-based ML workflows, driving 25\% lab-wide adoption within 1 year.
			\item Trained 10+ researchers on JAX/Flax workflows, achieving 25\% lab-wide adoption within 1 year through seminars and code reviews.
			      % \item Teaching Assistant for Discrete Mathematics and Probabilistic Graphical Models.
			\item Teaching Assistant for Discrete Mathematics (150+ undergrads) and Probabilistic Graphical Models (40+ grad students): Designed and graded final exams, assignments, and led tutorials.
		\end{itemize}
	}%
}

\cventry{
	\juneAbbrev{}--\augustAbbrev{} 2022
}{
	\iflanguage{french}{Ingénieur IA Stagiaire}{AI Engineer Intern}%
}{%
	Apex Solutions
}{%
	% Figeac
}{}{
	\iflanguage{french}{
		\begin{itemize}
			\item Conception d'environnements de simulation d'intrusions dans des infrastructures critiques et de benchmarks d'apprentissage par renforcement.%, toujours utilisés en recherche interne.
		\end{itemize}
	}{
		\begin{itemize}
			\item Prototyped a multi-agent simulation environment (Python/Gymnasium) for modeling intrusion scenarios in critical infrastructure; framework remains actively used for internal security research.
			\item Developed RL benchmarks for adversarial capture-the-flag simulations with limited information-sharing constraints (PyTorch/Stable-Baselines3).
			\item Optimized RL algorithms for red team (offense) and blue team (defense) agents, enhancing adversarial training in security-focused simulations.
		\end{itemize}
	}
}

\cventry{
	2021--2022
}{
	\iflanguage{french}{Président du Bureau des Arts}{Arts Council President}%
}{%
	École des Mines de Saint-Étienne
}{%
	% Saint-Étienne
}{}{
	\begin{itemize}
		\item \iflanguage{french}{
			      Gestion de la programmation culturelle, dont l'organisation de trois événements majeurs par mois et la coordination de la production du gala annuel. % réunissant plus de 100 artistes.
			      %   Nombre d'adhérents doublé en un an.
		      }{
			      %   Directed cultural programming and events, organizing three monthly events, including the school's annual gala featuring over 100 artists.
			      %   Expanded arts engagement through regular music, dance, and theater classes, doubling participant numbers over one year.
			      Led cultural programming for 500+ students, organizing 3+ monthly events (concerts, exhibitions) and coordinating the annual gala with 100+ artists.
			      Expanded arts engagement through workshops (music, dance, theater), doubling participation within 1 year.
		      }
	\end{itemize}
}
% \subsection{Miscellaneous}
% \cventry{year--year}{Job title}{Employer}{City}{}{Description}
